### 2012-12-04 inst/examples/policycosts/writeup.Rmd
updated writeup Fig4 graphs

```{r Figure4}
frac_lost <- seq(0.1,0.9, length=5)
out <- lapply(frac_lost, pdgControl:::fig4, ls())
out <- melt(out)
colnames(out) = c("statistic", "penalty", "value", "index")
out <- cbind(out[1:3], fraction__npv_lost = frac_lost[out$index])
Figure4 <- ggplot(out) + geom_point(aes(fraction_npv_lost, value, col=penalty)) + geom_line(aes(fraction, value, col=penalty)) + facet_wrap(~statistic, scales="free_y")
Figure4
````

>>>>

```{r Figure4}
frac_lost <- seq(0,1, length=20)
tmp <- lapply(frac_lost, fig4, ls())
out <- melt(tmp, id=c("reps", "var", "acor"))
colnames(out) = c("reps", "var", "acor", "nothing", "penalty", "index")
out <- cbind(out[c(1,2,3,5)], fraction = frac_lost[out$index])
out <- data.table(out)

Ev = out[,mean(var),by=c('penalty', 'fraction')]
SDv = out[,sd(var),by=c('penalty', 'fraction')]
Ea = out[,mean(acor),by=c('penalty', 'fraction')]
SDa = out[,sd(acor),by=c('penalty', 'fraction')]

tmp2 <- data.table(penalty = Ev$penalty, fraction = Ev$fraction, Ev = Ev$V1, Ea = Ea$V1, SDv=SDv$V1, SDa = SDa$V1)

Fig4a <- ggplot(tmp2, aes(fraction, Ev, ymin=Ev-SDv, ymax=Ev+SDv, col=penalty)) + 
  #geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.1) + 
  geom_line() + xlab("Fraction of NPV lost to costs")
Fig4a
Fig4b <- ggplot(tmp2, aes(fraction, Ea, ymin=Ea-SDa, ymax=Ea+SDa, col=penalty)) + 
  #geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.1) + 
  geom_line() + xlab("Fraction of NPV lost to costs")
Fig4b
````
